RQdraft1

### 2024-09-11 RQdraft1.Rmd
week1push-dptm

# Research Questions
RQ1a: 
  To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Computing Sciences at Radboud University?

>>>>

# Research Questions
RQ1a: 
  To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?
